\newpage

```{r appendixB_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))
```

```{r set_lakes_glimpse, echo = FALSE}
# can handle single or multiple lakes or lake arms for tabulation

lakes_glimpse <- sort(lakes_of_interest)                            # example of all key lakes (but will omit KCA, KMA, LongA, LongB!)
lakes_glimpse <- c("Kennedy Lake (Clay)", "Kennedy Lake (Main)")  # example of multiple lake arms
# lakes_glimpse <- c("Long Lake", "Long Lake (A)", "Long Lake (B)") # example of multiple lake arms
# lakes_glimpse <- sort(c("Cheewhat Lake", "Hobiton Lake"))           # example of multiple lakes
# lakes_glimpse <- c("Cheewhat Lake")                               # simple example of one lake
```

# APPENDIX `r new_appendix()`. ADDITIONAL METADATA {#app:additional}

Appendix B1 and B2 present information for a limited number of study lakes surveyed in the Lake Enrichment and Study Lakes programs; the associated data for all lakes can be obtained from the specified comma-delimited text files.

Appendix B1 presents the survey-specific acoustic sounder equipment employed, and displays the number of regular and surface trawls conducted and total trawl effort and catch. The data for all lakes can be found in AST_survey_summary.csv.

Appendix B2 presents the physical parameter metadata (location, transect number and length, stratum depth minimum and maximum, and total area associated with each stratum) used to scale up fish target data to estimates of fish abundance. The parameters for all study lakes can be found in lep_lake_parameters.csv.

```{r acoustic-gear-merge-setup} 

### visualizing the data - survey effort and acoustics gear Hyatt 2000 table 1
### based on actual lake codes in data (e.g., different lake arms treated separately)
### Create a survey_date in the trawl data set to merge with acoustic data

### Acoustic
acoustic_data_summary <- (Acoustic_data_import) %>%
# filter(lake_name %in% lakes_glimpse) %>%
  select(lake_name, lake_code, ats_year, survey_date, survey_month, sounder_type, sounder_gain, transect, targets) %>%
  distinct() %>%
  group_by(lake_name, lake_code, ats_year, survey_date, survey_month, sounder_type) %>%
  summarise(
  n_transects = n_distinct(transect),
  n_targets   = sum(targets, na.RM = TRUE),
  .groups = "drop")
  
trawl_data_summary <- (Trawl_data_import) %>%
# filter(lake_name %in% lakes_glimpse) %>%
  filter(!gear_info %in% "DUM2") %>%
  filter(!(life_stage %in% "Adult" & species_common_name %in% "Sockeye")) %>%
  mutate(survey_date = trawl_date) %>%
  group_by(
    lake_name,
    lake_code,
    ats_year,
    survey_date) %>%
  # trawl metrics
  summarise(n_trawls = n_distinct(trawl_number),
            n_surface_trawls    = n_distinct(trawl_number[depth_m == 0]),
            total_trawl_minutes = sum(calc_duration_time[!duplicated(trawl_number)], na.rm = TRUE),
            # fish counts
            n_Fish        = n(),
            n_Sockeye     = sum(species_common_name == "Sockeye",    na.rm = TRUE),
            n_Stickleback = sum(species_common_name == "Stickleback",na.rm = TRUE),
           .groups = "drop") %>%
  mutate("n_Others" = n_Fish - n_Sockeye - n_Stickleback) %>%
  arrange(lake_name,survey_date)

# join acoustic and trawl tables
acoustic_trawl_data_merge <- 
  full_join(trawl_data_summary, acoustic_data_summary,  
            by = c("lake_name", "lake_code", "ats_year", "survey_date"), 
            suffix = c("_Trawl", "_Acoustic")) %>%
  select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = survey_date, 
         "Sounder Type"  = sounder_type, "#Transects" = n_transects, "#Targets" = n_targets,
         "#Trawls" = n_trawls, "Surface Trawls" = n_surface_trawls, "Trawl Time (min)" = total_trawl_minutes,
         "#Fish" = n_Fish, "#Sockeye" = n_Sockeye, "#Stickleback" = n_Stickleback, "Others" = n_Others) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(`ATS Year` = as.character(`ATS Year`)) %>%
  arrange(Lake, Date)

# SAVE complete list of ATS survey meta- and summary data
# Create output directory if it doesn't already exist, then save
dir.create("02_final_output", showWarnings = FALSE, recursive = TRUE)
write.csv(
  acoustic_trawl_data_merge,
  file = file.path("02_final_output", "ATS_meta_summary_by_survey_date.csv"),
  row.names = FALSE)

# Create a summary table for sockeye, filtered for lakes_glimpse list
for (lk in lakes_glimpse) {  # filter down to one lake as specified at top  # lakes_of_interest) {
  
  df_lk <- filter(acoustic_trawl_data_merge, Lake == lk)
  
  Sockeye_summary_table <- df_lk %>%
    # #filter(species_common_name %in% "Sockeye", !is.na(sounder_type), !is.na(transect), !is.na(trawl_number)) %>% # filter only sockeye species
    # filter(species_common_name %in% "Sockeye") %>%                                        # filter for sockeye species
    # group_by(survey_date, ats_year, sounder_type) %>%
    # mutate(Transects_completed = ifelse(!is.na(transect), n_distinct(transect), 0L),      # store the max transect number in that lake, that date
    #        Trawls_completed = ifelse(!is.na(trawl_number), n_distinct(trawl_number), 0L), # count the distinct number of trawl events that day, in the specific lake
    #        Surface_trawl = ifelse(!is.na(trawl_number) & !is.na(depth_m), 
    #                               n_distinct(trawl_number[depth_m == 0]), 0L)) %>%        # extract only the trawl events when the depth was 0
    # select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = survey_date, "Sounder Type"  = sounder_type, 
    #        "#Transects" = Transects_completed, "#Trawls" = Trawls_completed, "Surface Trawls" = Surface_trawl) %>%
    # mutate(`ATS Year` = as.character(`ATS Year`)) %>%
    distinct()
  
  assign(paste0(lk, "_summary_table"), Sockeye_summary_table)
}
```

```{r appendixB1_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))
```
<!-- \newpage -->

### *AST Survey Summary Data*

```{r acoustic-gear-appendixB, tab.cap=appendixB_acoustic_trawl_summary_cpation}

tbl_name <- paste0(lakes_glimpse, "_summary_table")

# Retrieve and combine all tables
ft_table <- dplyr::bind_rows(
  lapply(tbl_name, get))

# Create flextable
ft <- flextable::flextable(ft_table) |>
  flextable::theme_booktabs() |>
  flextable::fontsize(size = 8, part = "all") |>
  flextable::padding(
    padding.top = 1,
    padding.bottom = 1,
    padding.left = .5,
    padding.right = .5,
    part = "all") |>
  flextable::separate_header() |>
  flextable::fontsize(size = 9, part = "header") |>
  flextable::align(
    align = "center",
    part = "all")

# Add separator lines between lakes
break_rows <- ft_table %>%
  mutate(rowid = row_number()) %>%
  group_by(Lake) %>%
  summarise(rowid = max(rowid), .groups = "drop") %>%
  pull(rowid)

ft <- flextable::hline(
  ft,
  i = break_rows,
  border = officer::fp_border(width = 1))

ft |>
  flextable::autofit()

```

```{r appendixB2_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))
```

```{r lake_strata_setup}
lake_strata_table <- read.csv("00_data/Lake_strata_length.csv") 
# rename(lake_name = Lake.name, lake_code = Lake.code)

# lake_strata_table_fix <- fix_lake_codes_names(lake_strata_table)

# extract the lakes in the dataset
lakes_in_acoustic <- sort(unique(Acoustic_data_import$lake_name)) # extract the lake names acoustic dataset
lakes_in_trawl    <- sort(unique(Trawl_data_import$lake_name))    # Extract the lake names trawl dataset

lakes_in_ATS_database <- c(lakes_in_acoustic, lakes_in_trawl)     # combine the lists
lakes_in_ATS_database <- sort(unique(lakes_in_ATS_database))
lakes_in_ATS_database <- lakes_in_ATS_database[!is.na(lakes_in_ATS_database)] # remove NAs

# Clean the lake strata table
lake_strata_table_ATS <- lake_strata_table %>%
  filter(Lake.name %in% lakes_in_ATS_database) %>%
  rename("Latitude"   = Lake.latitude, "Longitude" = Lake.longitude, "Lake" = Lake.name,
         "Length (m)" = Transect.length.m, "Area (ha)" = Area.ha, "Code" = Lake.code,
         "Depth (m).Min" = Depth.min.m, "Depth (m).Max" = Depth.max.m) %>%
  mutate(`Area (ha)`  = as.integer(`Area (ha)`),
         `Length (m)` = as.integer(`Length (m)`))

lake_strata_table_ATS$Latitude <- str_replace_all(lake_strata_table_ATS$Latitude, " deg", "°")
lake_strata_table_ATS$Latitude <- str_replace_all(lake_strata_table_ATS$Latitude, " min", "' N")

lake_strata_table_ATS$Longitude <- str_replace_all(lake_strata_table_ATS$Longitude, " deg", "°")
lake_strata_table_ATS$Longitude <- str_replace_all(lake_strata_table_ATS$Longitude, " min", "' W")

lake_strata_table_ATS <- lake_strata_table_ATS %>%
  select(Lake, Code, Latitude, Longitude, 
         Transect, 
        `Depth Min (m)` = `Depth (m).Min`, `Depth Max (m)` = `Depth (m).Max`, 
        `Length (m)`, `Area (ha)`) %>%
  arrange(Lake, Transect) %>%
  filter(!is.na(Transect))

# SAVE complete list of physical lake parameters for the AST lakes
# Create output directory if it doesn't already exist, then save
dir.create("02_final_output", showWarnings = FALSE, recursive = TRUE)
write.csv(
  lake_strata_table_ATS,
  file = file.path("02_final_output", "ATS_lake_strata_table.csv"),
  row.names = FALSE)

```
### *Lake Physical Parameters*

```{r lake-strata-table, tab.cap=appendixB_lake_strata_tab_caption}

ft_table <- lake_strata_table_ATS %>%
  filter(Lake %in% lakes_glimpse) %>%
  arrange(Lake, Transect)

ft <- flextable::flextable(ft_table) |>
  flextable::theme_booktabs() |>
  flextable::separate_header() |>
  flextable::fontsize(size = 9, part = "header") |>
  flextable::bold(part = "header") |>
  flextable::fontsize(size = 9, part = "body") |>
  flextable::align(align = "center", part = "all")

break_rows <- ft_table %>%
  mutate(rowid = row_number()) %>%
  group_by(Lake) %>%
  summarise(rowid = max(rowid), .groups = "drop") %>%
  pull(rowid)

ft <- flextable::hline(
  ft,
  i = break_rows,
  border = officer::fp_border(width = 1))

ft |>
  flextable::autofit()

```