\newpage

```{r appendixB_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))

lakes_of_interest <- "Cheewhat Lake"  # keeping it simple for this appendix [hs 260824]

```

# APPENDIX `r new_appendix()`. ADDITIONAL METADATA {#app:additional}

This appendix presents information about the acoustic gear equipment used in the Lake Enrichment and Study Lakes programs for key BC lakes, as well as the number of regular and surface trawls conducted across the ATS years. Additionally, an example of the metadata table for the lake strata is also provided.

```{r acoustic-gear-merge-setup} 
############ visualizing the data - survey effort and acoustics gear Hyatt 2000 table 1
### Create a survey_date in the trawl data set to merge with acoustic data

### Trawl
Trawl_data_renamed <- fix_lake_codes_names(Trawl_data_import) %>%
  mutate(survey_date = trawl_date)

# join acoustic and trawl tables
Trawl_acoustic_data <- full_join(Trawl_data_renamed, fix_lake_codes_names(Acoustic_data_import), 
                                 by = c("ats_year", "lake_code", "survey_date", "lake_name"), 
                                 suffix = c("_Trawl", "_Acoustic"))

# Filter lakes and species of interest
Trawl_acoustic_data <- Trawl_acoustic_data %>%
  filter(lake_name %in% lakes_of_interest,
         #species_common_name %in% c("Sockeye", "Stickleback"),
         !gear_info %in% "DUM2",
         !life_stage %in% "Adult")

# Clean columns keeping only columns of interest
Trawl_acoustic_data_clean <- Trawl_acoustic_data %>%
  select(ats_year, lake_code, lake_name, trawl_date, survey_date, trawl_month, survey_month, 
         trawl_number, depth_m, depth_min_m, depth_max_m, species_code,
         species_common_name, life_stage, age_class, source_files, 
         transect, targets, prop_sockeye, prop_stickleback, sounder_code, sounder_type, acoustic_source_file)

# Create a summary table for sockeye
for (lk in lakes_of_interest) {
  
  df_lk <- filter(Trawl_acoustic_data_clean, lake_name == lk)
  
  Sockeye_summary_table <- df_lk %>%
    #filter(species_common_name %in% "Sockeye", !is.na(sounder_type), !is.na(transect), !is.na(trawl_number)) %>% # filter only sockeye species
    filter(species_common_name %in% "Sockeye") %>% # filter only sockeye species
    group_by(survey_date, ats_year, sounder_type) %>%
    mutate(Transects_completed = ifelse(!is.na(transect), n_distinct(transect), 0L),  # store the max transect number in that lake, that date
           Trawls_completed = ifelse(!is.na(trawl_number), n_distinct(trawl_number), 0L),   # count the distinct number of trawl events that day, in the specific lake
           Surface_trawl = ifelse(!is.na(trawl_number) & !is.na(depth_m), 
                                  n_distinct(trawl_number[depth_m == 0]), 0L)) %>% # extract only the trawl events when the depth was 0
    select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = survey_date, "Sounder Type"  = sounder_type, 
           "#Transects" = Transects_completed, "#Trawls" = Trawls_completed, "Surface Trawls" = Surface_trawl) %>%
    mutate(`ATS Year` = as.character(`ATS Year`)) %>%
    distinct()
  
  assign(paste0(lk, "_summary_table"), Sockeye_summary_table)
}
```

```{r acoustic-gear-Cheewhat, tab.cap="Summary of Cheewhat Lake Sockeye ATS dates, transects and trawl completed, and acoustic gear."}

# Plot the table
flextable::flextable(`Cheewhat Lake_summary_table`)|>
  flextable::separate_header() |>
  flextable::align(align = "center", part = "all") |>
  flextable::autofit()

```



```{r landscape-lake-strata-table, tab.cap="Summary of the lake strata for key lakes as an example of the metadata available for the lakes surveyed during LEP. The complete table is available as a supplementary material."}
lake_strata_table <- read.csv("00_data/Lake_strata_length.csv")

# extract the lakes in the dataset
lakes_in_acoustic <- unique(fix_lake_codes_names(Acoustic_data_import)$lake_name) # extract the lake names acoustic dataset
lakes_in_trawl <- unique(fix_lake_codes_names(Trawl_data_import)$lake_name) # Extract the lake names trawl dataset

lakes_in_ATS_database <- c(lakes_in_acoustic, lakes_in_trawl) # combine the lists
lakes_in_ATS_database <- lakes_in_ATS_database[!is.na(lakes_in_ATS_database)] # remove NAs

lakes_in_ATS_database <- unique(lakes_in_ATS_database)

# Clean the lake strata table
lake_strata_table <- lake_strata_table %>%
  filter(Lake.name %in% lakes_in_ATS_database) %>%
  rename("Latitude" = Lake.latitude, "Longitude" = Lake.longitude, "Lake" = Lake.name,
         "Length (m)" = Transect.length.m, "Area (ha)" = Area.ha, "Code" = Lake.code,
         "Depth (m).Min" = Depth.min.m, "Depth (m).Max" = Depth.max.m) %>%
  mutate(`Area (ha)` = as.integer(`Area (ha)`),
         `Length (m)` = as.integer(`Length (m)`))

lake_strata_table$Latitude <- str_replace_all(lake_strata_table$Latitude, " deg", "°")
lake_strata_table$Latitude <- str_replace_all(lake_strata_table$Latitude, " min", "' N")

lake_strata_table$Longitude <- str_replace_all(lake_strata_table$Longitude, " deg", "°")
lake_strata_table$Longitude <- str_replace_all(lake_strata_table$Longitude, " min", "' W")

lake_strata_table <- lake_strata_table %>%
  select(Lake, Code, Latitude, Longitude, 
         Transect, 
         `Depth Min (m)` = `Depth (m).Min`, `Depth Max (m)` = `Depth (m).Max`, 
         `Length (m)`, `Area (ha)`) %>%
  arrange(Lake, Transect) %>%
  filter(Lake %in% lakes_of_interest,
         !is.na(Transect)) # , 
       # Transect <3, 
       # Lake %in% c("Great Central Lake", "Sproat Lake", "Henderson Lake", "Kennedy Lake (Main)", "Cheewhat Lake", "Muriel Lake", "Hobiton Lake"), 
       # `Depth (m).Min` < 10)

ft <- flextable::flextable(lake_strata_table) |>
  flextable::separate_header() |>
  flextable::align(align = "center", part = "all")

break_rows <- lake_strata_table |>
  mutate(rowid = row_number()) |>
  group_by(Lake) |>
  summarise(rowid = max(rowid)) |>
  pull(rowid)

ft <- flextable::hline(
  ft,
  i = break_rows,
  border = officer::fp_border(width = 1)
)

ft |> flextable::autofit()

# flextable::set_flextable_defaults(
#  font.size = 10,
#  padding.left = 3,
#  padding.right = 3,
#  padding.top = 1,
#  padding.bottom = 1,
#  na_str = "-",
#  theme_fun = "theme_booktabs"
# )

# # Plot the table
# flextable::flextable(lake_strata_table) |>
#   flextable::separate_header() |>
#   flextable::align(align = "center", part = "all") |>
#   flextable::autofit() #|>
#  #flextable::save_as_docx(
#  #"landscape lake strata table" = lake_strata_table, path = "./02_final_output/Lake strata table.docx")

```