\newpage

```{r appendixB_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))

lakes_glimpse <- "Kennedy Lake"  # keeping it simple for this appendix [hs 260824]

```

# APPENDIX `r new_appendix()`. ADDITIONAL METADATA {#app:additional}

Appendix B1 presents the survey-specific acoustic equipment (sounder) used in the Lake Enrichment and Study Lakes programs for one lake, and includes the number of regular and surface trawls conducted. The data for all other lakes can be found in XXXXXX.csv.

Appendix B2 presents the physical parameter metadata (location, transect number and length, stratum depth minimum and maximum, and total area associated with each stratum) used to scale up fish target data to estimates of fish abundance. The parameters for all other study lakes can be found in XXXXXX.csv.

```{r acoustic-gear-merge-setup} 

############ visualizing the data - survey effort and acoustics gear Hyatt 2000 table 1
### Create a survey_date in the trawl data set to merge with acoustic data

### Acoustic
acoustic_data_summary <- fix_lake_codes_names(Acoustic_data_import) %>%
# filter(lake_name %in% lakes_glimpse) %>%
  select(lake_name, lake_code, ats_year, survey_date, survey_month, sounder_type, sounder_gain, transect, targets) %>%
  distinct() %>%
  group_by(lake_name, lake_code, ats_year, survey_date, survey_month, sounder_type) %>%
  summarise(
  n_transects = n_distinct(transect),
  n_targets   = sum(targets, na.RM = TRUE),
  .groups = "drop")
  
trawl_data_summary <- fix_lake_codes_names(Trawl_data_import) %>%
# filter(lake_name %in% lakes_glimpse) %>%
  filter(!gear_info %in% "DUM2") %>%
  filter(!(life_stage %in% "Adult" & species_common_name %in% "Sockeye")) %>%
  mutate(survey_date = trawl_date) %>%
  group_by(
    lake_name,
    lake_code,
    ats_year,
    survey_date) %>%
  # trawl metrics
  summarise(n_trawls = n_distinct(trawl_number),
            n_surface_trawls    = n_distinct(trawl_number[depth_m == 0]),
            total_trawl_minutes = sum(unique(calc_duration_time), na.rm = TRUE),
            # fish counts
            n_Fish        = n(),
            n_Sockeye     = sum(species_common_name == "Sockeye",    na.rm = TRUE),
            n_Stickleback = sum(species_common_name == "Stickleback",na.rm = TRUE),
           .groups = "drop") %>%
  mutate("n_Others" = n_Fish - n_Sockeye - n_Stickleback) %>%
  arrange(lake_name,survey_date)

# join acoustic and trawl tables
acoustic_trawl_data_merge <- 
  full_join(trawl_data_summary, acoustic_data_summary,  
            by = c("lake_name", "lake_code", "ats_year", "survey_date"), 
            suffix = c("_Trawl", "_Acoustic")) %>%
  select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = survey_date, 
         "Sounder Type"  = sounder_type, "#Transects" = n_transects, "#Targets" = n_targets,
         "#Trawls" = n_trawls, "Surface Trawls" = n_surface_trawls, "Trawl Time (min)" = total_trawl_minutes,
         "#Fish" = n_Fish, "#Sockeye" = n_Sockeye, "#Stickleback" = n_Stickleback, "Others" = n_Others) %>%
  mutate(Date = as.Date(Date)) %>%
  mutate(`ATS Year` = as.character(`ATS Year`)) %>%
  arrange(Lake, Date)

##############################  CONTINUE HERE

# Create a summary table for sockeye
for (lk in lakes_glimpse) {  # filter down to one lake as specified at top  # lakes_of_interest) {
  
  df_lk <- filter(acoustic_trawl_data_merge, Lake == lk)
  
  Sockeye_summary_table <- df_lk %>%
    # #filter(species_common_name %in% "Sockeye", !is.na(sounder_type), !is.na(transect), !is.na(trawl_number)) %>% # filter only sockeye species
    # filter(species_common_name %in% "Sockeye") %>%                                        # filter for sockeye species
    # group_by(survey_date, ats_year, sounder_type) %>%
    # mutate(Transects_completed = ifelse(!is.na(transect), n_distinct(transect), 0L),      # store the max transect number in that lake, that date
    #        Trawls_completed = ifelse(!is.na(trawl_number), n_distinct(trawl_number), 0L), # count the distinct number of trawl events that day, in the specific lake
    #        Surface_trawl = ifelse(!is.na(trawl_number) & !is.na(depth_m), 
    #                               n_distinct(trawl_number[depth_m == 0]), 0L)) %>%        # extract only the trawl events when the depth was 0
    # select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = survey_date, "Sounder Type"  = sounder_type, 
    #        "#Transects" = Transects_completed, "#Trawls" = Trawls_completed, "Surface Trawls" = Surface_trawl) %>%
    # mutate(`ATS Year` = as.character(`ATS Year`)) %>%
    distinct()
  
  assign(paste0(lk, "_summary_table"), Sockeye_summary_table)
}
```

```{r acoustic-gear-appendixB, tab.cap=acoustic_meta_cap}

tbl_name <- paste0(lakes_glimpse, "_summary_table")

flextable::flextable(get(tbl_name)) |>
  flextable::separate_header() |>
  flextable::align(align = "center", part = "all") |>
  flextable::autofit()

# Plot the table
# flextable::flextable(paste0("`", lakes_glimpse, "_summary_table`"))|>
#   flextable::separate_header() |>
#   flextable::align(align = "center", part = "all") |>
#   flextable::autofit()

```


```{r landscape-lake-strata-table, tab.cap="Summary of the lake strata for key lakes as an example of the metadata available for the lakes surveyed during LEP. The complete table is available as a supplementary material."}
lake_strata_table <- read.csv("00_data/Lake_strata_length.csv")

# extract the lakes in the dataset
lakes_in_acoustic <- unique(fix_lake_codes_names(Acoustic_data_import)$lake_name) # extract the lake names acoustic dataset
lakes_in_trawl <- unique(fix_lake_codes_names(Trawl_data_import)$lake_name) # Extract the lake names trawl dataset

lakes_in_ATS_database <- c(lakes_in_acoustic, lakes_in_trawl) # combine the lists
lakes_in_ATS_database <- lakes_in_ATS_database[!is.na(lakes_in_ATS_database)] # remove NAs

lakes_in_ATS_database <- unique(lakes_in_ATS_database)

# Clean the lake strata table
lake_strata_table <- lake_strata_table %>%
  filter(Lake.name %in% lakes_in_ATS_database) %>%
  rename("Latitude" = Lake.latitude, "Longitude" = Lake.longitude, "Lake" = Lake.name,
         "Length (m)" = Transect.length.m, "Area (ha)" = Area.ha, "Code" = Lake.code,
         "Depth (m).Min" = Depth.min.m, "Depth (m).Max" = Depth.max.m) %>%
  mutate(`Area (ha)` = as.integer(`Area (ha)`),
         `Length (m)` = as.integer(`Length (m)`))

lake_strata_table$Latitude <- str_replace_all(lake_strata_table$Latitude, " deg", "°")
lake_strata_table$Latitude <- str_replace_all(lake_strata_table$Latitude, " min", "' N")

lake_strata_table$Longitude <- str_replace_all(lake_strata_table$Longitude, " deg", "°")
lake_strata_table$Longitude <- str_replace_all(lake_strata_table$Longitude, " min", "' W")

lake_strata_table <- lake_strata_table %>%
  select(Lake, Code, Latitude, Longitude, 
         Transect, 
         `Depth Min (m)` = `Depth (m).Min`, `Depth Max (m)` = `Depth (m).Max`, 
         `Length (m)`, `Area (ha)`) %>%
  arrange(Lake, Transect) %>%
  filter(Lake %in% lakes_of_interest,
         !is.na(Transect)) # , 
       # Transect <3, 
       # Lake %in% c("Great Central Lake", "Sproat Lake", "Henderson Lake", "Kennedy Lake (Main)", "Cheewhat Lake", "Muriel Lake", "Hobiton Lake"), 
       # `Depth (m).Min` < 10)

ft_table <- lake_strata_table %>% filter(lake %in% c(lakes_glimpse))
                                         
ft <- flextable::flextable(ft_table) |>
  flextable::separate_header() |>
  flextable::align(align = "center", part = "all")

break_rows <- lake_strata_table |>
  mutate(rowid = row_number()) |>
  group_by(Lake) |>
  summarise(rowid = max(rowid)) |>
  pull(rowid)

ft <- flextable::hline(
  ft,
  i = break_rows,
  border = officer::fp_border(width = 1)
)

ft |> flextable::autofit()

# flextable::set_flextable_defaults(
#  font.size = 10,
#  padding.left = 3,
#  padding.right = 3,
#  padding.top = 1,
#  padding.bottom = 1,
#  na_str = "-",
#  theme_fun = "theme_booktabs"
# )

# # Plot the table
# flextable::flextable(lake_strata_table) |>
#   flextable::separate_header() |>
#   flextable::align(align = "center", part = "all") |>
#   flextable::autofit() #|>
#  #flextable::save_as_docx(
#  #"landscape lake strata table" = lake_strata_table, path = "./02_final_output/Lake strata table.docx")

```