
\newpage

```{r appendix_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))

# lakes_of_interest <- c("Great Central Lake", "Hobiton Lake", "Kennedy Lake", "Long Lake")# TEST SET

```
# APPENDIX `r new_appendix()`. BIOLOGICAL DATA {#app:biology}

This appendix presents tables with trawl biosample and acoustic target metadata. 

### *Total ATS Trips by Lake and Year*

```{r survey-effort-table, tab.cap=ATS_trips, out.width=out_width}

survey_effort_table_import <- read.csv("00_data/Trip_effort_table_acoustic_trawl.csv", check.names = FALSE) %>%
  rename(lake_name = `Lake name`)

survey_effort_table_unique <- trim_lake_names(survey_effort_table_import) %>%
  group_by(lake_name) %>%
  summarise(
    across(
      where(is.numeric),
      ~ sum(.x, na.rm = TRUE)),
    .groups = "drop")

# Add total row
survey_effort_table_unique <- survey_effort_table_unique %>%
  bind_rows(
    survey_effort_table_unique %>%
      summarise(
        across(
          where(is.numeric),
          ~ sum(.x, na.rm = TRUE))) %>%
      mutate(lake_name = "Total") %>%
      select(lake_name, everything())) %>%
    rename(Lake = lake_name)


# survey_effort_table <- trim_lake_names(survey_effort_table_import) %>%
#   bind_rows(survey_effort_table %>%
#               summarise(across(where(is.integer), ~ sum(.x, na.rm = TRUE)), lake_name = "Total")) %>%
#   select(1,names(.)[-1][order(as.integer(names(.)[-1]))])

flextable::set_flextable_defaults(font.size = 6)

# Plot the table
flextable::flextable(survey_effort_table_unique)|>
  flextable::rotate(part = "header", rotation = "btlr", j = 2:ncol(survey_effort_table_unique)) |>
  flextable::autofit() |>
  flextable::height(i = 1, height = 0.5, part = "header") |>
  flextable::hrule(rule = "exact", part = "header")

```

\newpage
### *Total Sockeye Captured in Trawls, by Lake and Year*

```{r sockeye_info, tab.cap=biosample_sox_count, out.width=out_width}

Trawl_summary_sockeye <- trim_lake_names(fix_lake_codes_names(Trawl_data_import)) %>%
  filter(species_common_name == "Sockeye") %>%
  group_by(lake_name, ats_year) %>%
  summarise(fish_count = n(), .groups = "drop") -> sockeye_summary_table

# Pivot to wide format
summary_table_sockeye_class_total <- sockeye_summary_table %>%
pivot_wider(names_from = ats_year,
            values_from = fish_count,
            values_fill = 0)

# Add total row per year
summary_table_sockeye_class_total <- summary_table_sockeye_class_total %>%
  #bind_rows(summary_table_sockeye_class_total) %>%
             # summarise(across(where(is.numeric), sum), lake_name = "Total")) %>%
   rename("Lake" = lake_name)

flextable::set_flextable_defaults(font.size = 6)

# Plot the table
flextable::flextable(summary_table_sockeye_class_total) |>
  flextable::autofit()

```

\newpage
### *Total Non-Sockeye Captured in Trawls, by Lake and Year*

```{r other_fish_info, tab.cap=biosam_nonsox_count, out.width=out_width}

Trawl_summary_non_sockeye <- trim_lake_names(fix_lake_codes_names(Trawl_data_import)) %>% 
  filter(species_common_name != "Sockeye") %>%
  group_by(lake_name, ats_year) %>%
  summarise(fish_count = n(), .groups = "drop") -> non_sockeye_summary_table

# Pivot to wide format
summary_table_fish_class_total <- non_sockeye_summary_table %>%
pivot_wider(names_from = ats_year,
            values_from = fish_count,
            values_fill = 0)

# Add total row per year
summary_table_fish_class_total <- summary_table_fish_class_total %>%
  #bind_rows(summary_table_fish_class_total %>%
             # summarise(across(where(is.numeric), sum), lake_name = "Total")) %>%
  select(1,names(.)[-1][order(as.numeric(names(.)[-1]))]) %>%
   rename("Lake" = lake_name)

# block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))

flextable::set_flextable_defaults(font.size = 6)

# Plot the table
flextable::flextable(summary_table_fish_class_total) |>
  flextable::autofit()

```
\newpage

```{r trawl-sox-stix-setup}
# Assemble Sox & Stix Trawl catch ----

# Filter the lakes and species of interest
Trawl_data_loi <- (fix_lake_codes_names(Trawl_data_import)) %>%
  filter(lake_name %in% lakes_of_interest,
         species_common_name %in% c("Sockeye", "Stickleback"),
         !is.na(fish_length_mm), !is.na(fish_weight_g), 
         !gear_info %in% "DUM2") %>%
  mutate(char_date = format(as.Date(trawl_date), "%d%b%y")) %>%
  select(-depth_m, - orig_start_time, -orig_end_time, -orig_duration_minutes, -orig_std_weight_g, -calc_end_time, -calc_duration_time, -calc_std_weight_g, -calc_K_factor, -general_comments, -preservative_code, -preservative_description, -preservative_description_short, -trawl_month, -trawl_unique_ID, -fish_unique_ID, -gear_info, -gear_type, -data_issues, -program_notes, -age_class, -weight_conversion_formula, -sas_scale, -sas_scale_book, -dat_scale_book, -dat_scale_book_letter, -species_code, -species_info_code, -aging_technique)

# Create a table specific for sockeye and count the number of trawls per lake, date and year
# Sockeye
Sockeye_catch_table <- Trawl_data_loi %>%
  filter(species_common_name %in% "Sockeye", life_stage %in% "Fry") %>% # filter only sockeye species
  group_by(trawl_date, ats_year, lake_name) %>%
  mutate(Trawls_hauls = ifelse(!is.na(trawl_number), n_distinct(trawl_number), 0L),   # count the distinct number of trawl events that day, in the specific lake
         Sockeye_fry = n())  # extract the number of sockeye fry collected

# Calculate the stats for the length and weight
Sockeye_catch_summary <- Sockeye_catch_table %>%
  group_by(lake_name, trawl_date, ats_year) %>%
  mutate(n_total = Sockeye_fry, 
         mean_length_mm = round(mean(fish_length_mm, na.rm = TRUE), 1),
         sd_length = sd(fish_length_mm, na.rm = TRUE),
         se_length = round(sd_length / sqrt(n_total), 2),
         moe_length = round(qt(0.975, df= n_total - 1) * se_length,2)) %>%
  mutate(n_total = Sockeye_fry,
         mean_weight_g = round(mean(fish_weight_g, na.rm = TRUE), 2),
         sd_weight = sd(fish_weight_g, na.rm = TRUE),
         se_weight = round(sd_weight / sqrt(n_total), 2),
         moe_weight = round(qt(0.975, df= n_total - 1) * se_weight, 2)) %>%
  filter(!moe_weight %in% "NaN") %>%
  ungroup()

# Create one table for each lake
sockeye_tables <- list()

for (lk in lakes_of_interest) {
  
  df_lk <- trim_lake_names(filter(Sockeye_catch_summary, lake_name == lk))
  
  Sockeye_catch <- df_lk %>%
    # select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = trawl_date, "Sockeye Fry_Trawls" = Trawls_hauls, 
    #      "Sockeye Fry_Catch (n)" = Sockeye_fry, "Sockeye Fry_Mean Length (mm)" = mean_length_mm, 
    #      "Sockeye Fry_95% MoE (mm)" = moe_length, "Sockeye Fry_Weight (g)" = mean_weight_g,
    #      "Sockeye Fry_95% MoE (g)" = moe_weight) %>%
    select("Lake" = lake_name, "ATS Year" = ats_year, "Date" = trawl_date, 
           "Sockeye Fry_Trawls"         = Trawls_hauls, 
           "Sockeye Fry_Catch (N)"      = Sockeye_fry,  "Sockeye Fry_Mean Length (mm)" = mean_length_mm, 
           "Sockeye Fry_SE Length (mm)" = se_length,    "Sockeye Fry_Mean Weight (g)"  = mean_weight_g,
           "Sockeye Fry_SE Weight (g)"  = se_weight) %>%
    distinct()
  
  # assign(paste0(lk, "_sockeye_catch_table"), Sockeye_catch)   # <-- not advised
  sockeye_tables[[lk]] <- Sockeye_catch
}

# Create a table specific for Stickleback and count the number of trawls per lake, date and year
Stickleback_catch_table <- Trawl_data_loi %>%
  filter(species_common_name %in% "Stickleback") %>% # filter only Stickleback species
  group_by(trawl_date, ats_year, lake_name) %>%
  mutate(Trawls_hauls = ifelse(!is.na(trawl_number), n_distinct(trawl_number), 0L),   # count the distinct number of trawl events that day, in the specific lake
         Stickleback_all = n())  # extract the number of sockeye fry collected

# Calculate the stats for the length and weight
Stickleback_catch_summary <- Stickleback_catch_table %>%
  group_by(lake_name, trawl_date, ats_year) %>%
  mutate(n_total = Stickleback_all, 
         mean_length_mm = round(mean(fish_length_mm, na.rm = TRUE), 1),
         sd_length = sd(fish_length_mm, na.rm = TRUE),
         se_length = round(sd_length / sqrt(n_total), 2),
         moe_length = round(qt(0.975, df= n_total - 1) * se_length,2)) %>%
  mutate(n_total = Stickleback_all,
         mean_weight_g = round(mean(fish_weight_g, na.rm = TRUE), 2),
         sd_weight = sd(fish_weight_g, na.rm = TRUE),
         se_weight = round(sd_weight / sqrt(n_total), 2),
         moe_weight = round(qt(0.975, df= n_total - 1) * se_weight, 2)) %>%
  filter(!moe_weight %in% "NaN") %>%
  ungroup()

# Create one table for each lake
  stickle_tables <- list()

for (lk in lakes_of_interest) {
  
  df_lk <- trim_lake_names(filter(Stickleback_catch_summary, lake_name == lk))
  
  Stickle_catch <- df_lk %>%
    select("lake_stix" = lake_name, "ATS Year" = ats_year, "Date" = trawl_date, 
           "Stickleback_Trawls"         = Trawls_hauls, 
           "Stickleback_Catch (N)"      = Stickleback_all, "Stickleback_Mean Length (mm)" = mean_length_mm, 
           "Stickleback_SE Length (mm)" = se_length,       "Stickleback_Mean Weight (g)"  = mean_weight_g,
           "Stickleback_SE Weight (g)"  = se_weight) %>%
    distinct()
  
# assign(paste0(lk, "_stickle_catch_table"), Stickle_catch)  # <-- not advised
  stickle_tables[[lk]] <- Stickle_catch
}

```
```{r appendixA_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))
```

<!-- \newpage -->
### *Biosample Summary from Trawl Catch for Key Lakes by ATS Year*

```{r CHE-trawl-sox-stix-print, tab.cap=trawl_biosample_CHE}
# Generate trawl tables for lakes included in lakes_of_interest ---- 
if ("Cheewhat Lake" %in% lakes_of_interest) make_catch_table_list("Cheewhat Lake")
```
\newpage
```{r GCL-trawl-sox-stix-print, tab.cap=trawl_biosample_GCL}
if ("Great Central Lake" %in% lakes_of_interest) make_catch_table_list("Great Central Lake")  
```
\newpage
```{r HEN-trawl-sox-stix-print, tab.cap=trawl_biosample_HEN}
if ("Henderson Lake" %in% lakes_of_interest) make_catch_table_list("Henderson Lake")
```

\newpage
```{r HOB-trawl-sox-stix-print, tab.cap=trawl_biosample_HOB}
if ("Hobiton Lake" %in% lakes_of_interest) make_catch_table_list("Hobiton Lake")
```

```{r appendixAA_landscape, echo=FALSE}
block_section(prop_section(page_size = page_size(orient = "landscape"), type = "nextPage"))
```

\newpage
```{r KEN-trawl-sox-stix-print, tab.cap=trawl_biosample_KEN}
if ("Kennedy Lake" %in% lakes_of_interest) make_catch_table_list("Kennedy Lake") 
```
\newpage
```{r LON-trawl-sox-stix-print, tab.cap=trawl_biosample_LON}
if ("Long Lake" %in% lakes_of_interest) make_catch_table_list("Long Lake") 
```
\newpage
```{r MEZ-trawl-sox-stix-print, tab.cap=trawl_biosample_MEZ}
if ("Meziadin Lake" %in% lakes_of_interest) make_catch_table_list("Meziadin Lake") 
```
\newpage
```{r MUR-trawl-sox-stix-print, tab.cap=trawl_biosample_MUR}
if ("Muriel Lake" %in% lakes_of_interest) make_catch_table_list("Muriel Lake") 
```
\newpage
```{r NIM-trawl-sox-stix-print, tab.cap=trawl_biosample_NIM}
if ("Nimpkish Lake" %in% lakes_of_interest) make_catch_table_list("Nimpkish Lake") 
```
\newpage
```{r OWI-trawl-sox-stix-print, tab.cap=trawl_biosample_OWI}
if ("Owikeno Lake" %in% lakes_of_interest) make_catch_table_list("Owikeno Lake") 
```
\newpage
```{r SKI-trawl-sox-stix-print, tab.cap=trawl_biosample_SKI}
if ("Skidegate Lake" %in% lakes_of_interest) make_catch_table_list("Skidegate Lake") 
```
\newpage
```{r SPR-trawl-sox-stix-print, tab.cap=trawl_biosample_SPR}
if ("Sproat Lake" %in% lakes_of_interest) make_catch_table_list("Sproat Lake") 
```
\newpage
```{r TAH-trawl-sox-stix-print, tab.cap=trawl_biosample_TAH}
if ("Tahltan Lake" %in% lakes_of_interest) make_catch_table_list("Tahltan Lake") 
```
\newpage
```{r VER-trawl-sox-stix-print, tab.cap=trawl_biosample_VER}
if ("Vernon Lake" %in% lakes_of_interest) make_catch_table_list("Vernon Lake") 
```
\newpage
```{r WOS-trawl-sox-stix-print, tab.cap=trawl_biosample_WOS}
if ("Woss Lake" %in% lakes_of_interest) make_catch_table_list("Woss Lake") 
```
\newpage
```{r YAK-trawl-sox-stix-print, tab.cap=trawl_biosample_YAK}
if ("Yakoun Lake" %in% lakes_of_interest) make_catch_table_list("Yakoun Lake") 
```

```{r portrait_end, echo=FALSE}
# Add a portrait section after to "close" the landscape mode
block_section(prop_section(page_size = page_size(orient = "portrait"), type = "nextPage"))
```

